Macro Impacts

### 2016-08-03 Macro Impacts Revised.tex
nice analysis

$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = f\times (b^2-a^2)$. If $f$ is the triangle from section 2, then $A = \f16\Delta r(3r_0 + 2\Delta r)$.

>>>>

$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = f\times (b^2-a^2)$. If $f$ is the triangle from section 2, then $A = \f16\Delta r(3r_0 + 2\Delta r)$. When $T$ is zero, we get the result from section 2, which goes approximately as $k_0^2$. A quick plot of $E_m'$ shows that it goes as $k_0^2$ for small $k_0$ but asymptotes to a constant value. This constant value is achieved slower for larger $Q$ (or smaller $T$). In essence, this shows how the higher frequency terms stop contributing, and the small $k$ terms dominate.
